\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-04-08 bmc.tex
.
simplifying notation and consistency

\section{Model Checking}

As a final step, the enriched graph is model checked for the given
safety property. If a counter-example is found, it is simulated using
the $\simulate$ function and if reproducible, a violation is
concluded. In all other cases the falsification results in an
`unknown' result.

@@

We now describe the pesented technique using the Van der Pol
oscillator benchmark from~\cite{zutshi2014multiple}. Simulations
generated using uniformly random samples are shown in
\figref{vdp-cont}. We want to check the property $P_3$, indicated by
the red box, given the initial set indicated by the green box. The
abstraction is defined by $\quant_{0.2}(\x)$, which results in an
evenly gridded state-space, where each cell is of size $0.2 \times
0.2$ units.  Scatter-and-simulate is then used to construct the
abstract graph $G$, using $2$ samples per cell and the time step
$\Delta = 0.1s$. The complete process follows.

>>>>

% \section{Model Checking}

\mypara{Model Checking}
As a final step, the enriched graph is model checked for the given
safety property. If a counter-example is found, it is simulated using
the $\simulate$ function and if reproducible, a violation is
concluded. In all other cases the falsification results in an
`unknown' result.

@@

We now describe the presented technique using the Van der Pol
oscillator benchmark from~\cite{zutshi2014multiple}. Simulations
generated using uniformly random samples are shown in
\figref{vdp-cont}. We want to check the property $P_3$, indicated by
the red box, given the initial set indicated by the green box. The
abstraction is defined by $\quant_{0.2}(\x)$, which results in an
evenly gridded state-space, where each cell is of size $0.2 \times
0.2$ units.  Scatter-and-simulate is then used to construct the
abstract graph $G$, using $2$ samples per cell and the time step
$\Delta = 0.1s$. The complete process follows.

### 2017-04-08 implementation.tex

PWA-Rel was implemented in Python. Its different parts comprised of
the (a) abstraction graph generation, (b) regeression analysis and (c)
BMC. S3CAM was used to compute (a). To compute (b), OLS regression
routines were used from Scikit-learn~\cite{pedregosa2011scikit}, a
Python module for machine learning. Finally, the The bounded model
checking (c) was done using the SAL model checker~\cite{SAL-SRI},
which used Yices2~\cite{dutertre2014yices} as the SMT solver. A naive
alternative linear programming (LP) based model checker specific to the PWA
relational abstractions was implemented utilizing PyGLPK.

@@

We tabulate our preliminary evaluation in \tabref{res-rel}. We used
the more difficult benchmarks described in \cite{zutshi2014multiple},
including the Van der Pol oscillator, Brusselator, Lorenz attractor
and the Navigation benchmark. PWA-Rel and S3CAM were ran $10$ times
with different seeds and the running times were averaged. We tabulate
both the total time taken by PWA-Rel+SAL and PWA-Rel+LP to compute the
counter-example and compare against an implementation of S3CAM.
Different abstraction parameters are used for S3CAM and PWA-Rel, due
to the differences in which they operate. PWA-Rel requires a finer
abstraction to begni with in order to minimize the modeling errors.
On the other hand, a coarser abstraction as the intital abstraction is
works better for S3CAM due to the expensive refinement procedure
involved.

@@

As apparent form the results, the performance is comparable in all
benchmarks, but the last one: bouncing ball. PWA-Rel determines it to
be `safe' as it can not find a counter-example in the PWA relational
model. Also, apparent froom the results, PWA-Rel is more scalale with
the LP solver and PWA-Rel+SAL times out on most of the benchmarks.
The efficiency of the naive LP solver can be attributed to the careful
selection of the pareters for S3CAM (finer abstraction), resulting in
a small subgraph which can be easily explored for all paths.

>>>>

PWA-Rel was implemented in Python. Its different parts comprised of
the (a) abstraction graph generation, (b) regression analysis and (c)
BMC. S3CAM was used to compute (a). To compute (b), OLS regression
routines were used from Scikit-learn~\cite{pedregosa2011scikit}, a
Python module for machine learning. Finally, the The bounded model
checking (c) was done using the SAL model checker~\cite{SAL-SRI},
which used Yices2~\cite{dutertre2014yices} as the SMT solver. A naive
alternative linear programming (LP) based model checker specific to the PWA
relational abstractions was implemented utilizing PyGLPK.

@@

We tabulate our preliminary evaluation in \tabref{res-rel}. We used
the more difficult benchmarks described in \cite{zutshi2014multiple},
including the Van der Pol oscillator, Brusselator, Lorenz attractor
and the Navigation benchmark. PWA-Rel and S3CAM were ran $10$ times
with different seeds and the running times were averaged. We tabulate
both the total time taken by PWA-Rel+SAL and PWA-Rel+LP to compute the
counter-example and compare against an implementation of S3CAM.
Different abstraction parameters are used for S3CAM and PWA-Rel, due
to the differences in which they operate. PWA-Rel requires a finer
abstraction to begin with in order to minimize the modeling errors.
On the other hand, a coarser abstraction as the initial abstraction is
works better for S3CAM due to the expensive refinement procedure
involved.

@@

As apparent form the results, the performance is comparable in all
benchmarks, but the last one: bouncing ball. PWA-Rel determines it to
be `safe' as it can not find a counter-example in the PWA relational
model. Also, apparent from the results, PWA-Rel is more scalable with
the LP solver and PWA-Rel+SAL times out on most of the benchmarks.
The efficiency of the naive LP solver can be attributed to the careful
selection of the parameters for S3CAM (finer abstraction), resulting in
a small subgraph which can be easily explored for all paths.
